Non-kissing complexes and tau-tilting \\ for gentle algebras

### 2018-07-13 firstPaper/firstPaperLong/nonKissingComplex.tex
update Fig 21 and references

\begin{proof}
If~$\omega$ is not maximal in~$F$ for~$\prec_\alpha$, let~${\mu \eqdef \min_{\prec_\alpha} \set{\nu \in F_\alpha}{\omega \prec_\alpha \nu}}$.
Let~$\sigma$ denote the maximal common substring of~$\omega$ and~$\mu$ containing~$\alpha$.
Since~$\omega$ and~$\mu$ are distinct, they split at an endpoint of~$\sigma$.
At this endpoint, the arrow~$\beta$ of~$\omega$ not in~$\sigma$ points in the same direction as~$\alpha$ since~$\omega \prec_\alpha \mu$.
Let~$\lambda$ be maximal in~$F$ for~$\prec_\beta$.
If~$\lambda \ne \omega$, then~$\lambda$ either kisses~$\mu$ or contradicts the minimality of~$\mu$ among the walks~$\set{\nu \in F_\alpha}{\omega \prec_\alpha \nu}$.
See \fref{fig:pure}\,(right) for an illustration.
We conclude that~$\lambda = \omega$ has a distinguished arrow~$\beta$ in the direction of~$\alpha$.
\end{proof}

@@

\begin{proof}
In view of Lemma~\ref{lem:distArrowExist}, it remains to prove that each walk of~$F$ contains at most one distinguished arrow in each direction.
Assume that a walk~$\omega$ has two distinguished arrows~$\alpha, \beta$ pointing in the same direction.
Orient~$\omega$ in this same direction and assume without loss of generality that~$\alpha$ appears before~$\beta$ along~$\omega$.
%Note that we also allow a priori~$\alpha, \beta$ to be different occurrences along~$\omega$ of the same arrow of~$Q\blossom_1$.
Let~$\gamma$ be the incoming arrow at~$v \eqdef s(\beta)$ such that~$\gamma\beta \in I$.
Let~$\nu \eqdef \distinguishedWalk{\gamma}{F}$ denote the distinguished walk of~$F$ at~$\gamma$, considered oriented backward~$\gamma$.
We denote by~$\sigma$ the maximal common substring of~$\omega$ and~$\nu$ (it can be reduced to~$\varepsilon_v$).
Note that~$\sigma$ cannot contain~$\alpha$ since otherwise we would have~$\omega \prec_\alpha \nu$ contradicting the assumption that~$\omega = \distinguishedWalk{\alpha}{F}$. 
Since~$\omega$ and~$\nu$ are non-kissing, $\omega$ (resp.~$\nu$) enters~$\sigma$ with an incoming (resp.~outgoing) arrow.
Let~$\mu \eqdef \omega[\,\cdot\,, v] \, \nu[v, \cdot\,]$ be the walk connecting~$s(\omega)$ to~$t(\nu)$ via~$v$, using the prefix of~$\omega$ ending at~$v$ followed by the suffix of~$\nu$ starting at~$v$.
All these notations are illustrated in \fref{fig:pure}\,(left).
We claim that~$\mu$ is non-kissing with any walk of~$F$, contradicting the maximality~of~$F$.

Assume for the sake of contradiction that there is~$\lambda \in F$ such that~$\lambda$ and~$\mu$ are kissing.
Let~$\tau$ be a maximal common substring of~$\lambda$ and~$\mu$ where they kiss.
Since~$\lambda$ does not kiss~$\omega$ nor~$\nu$ (as they all belong to~$F$), we obtain that~$\tau$ contains~$v$ and strictly contains~$\sigma$.
%To prove this claim, observe first that~$\mu$ is non-kissing with~$\omega$ and~$\nu$ (since~$\omega$ and~$\nu$ are non-kissing).
%Consider another walk~$\lambda \in F$ and assume that~$\lambda$ and~$\mu$ are kissing.
%Note that the maximal common substring~$\tau$ of~$\omega$ and~$\lambda$ containing~$v$ is non-empty (otherwise~$\lambda$ would kiss~$\omega$ or~$\nu$) and contains strictly~$\sigma$ (otherwise~$\lambda$ would kiss~$\nu$).
We now distinguish two cases (see \fref{fig:pure}\,(left)):
\begin{enumerate}[(i)]
\item If~$\lambda$ passes through~$\beta$, then it enters~$\tau$ with an outgoing arrow (since it kisses~$\mu$), contradicting the maximality of~$\omega$~in~$\prec_\beta$.
\item If~$\lambda$ passes through~$\gamma$, then it enters~$\sigma$ with an incoming arrow (since~$\tau$ strictly contains~$\sigma$), contradicting the maximality of~$\nu$ in~$\prec_\gamma$. 
\end{enumerate}
We obtained a contradiction in all cases, which shows that~$\mu$ is non-kissing with any other walk~of~$F$.

>>>>

\begin{proof}
If~$\omega$ is not maximal in~$F$ for~$\prec_\alpha$, let~${\mu \eqdef \min_{\prec_\alpha} \set{\nu \in F_\alpha}{\omega \prec_\alpha \nu}}$.
Let~$\sigma$ denote the maximal common substring of~$\omega$ and~$\mu$ containing~$\alpha$.
Since~$\omega$ and~$\mu$ are distinct, they split at an endpoint of~$\sigma$.
At this endpoint, the arrow~$\beta$ of~$\omega$ not in~$\sigma$ points in the same direction as~$\alpha$ since~$\omega \prec_\alpha \mu$.
Let~$\lambda$ be maximal in~$F$ for~$\prec_\beta$.
If~$\lambda \ne \omega$, then~$\lambda$ either kisses~$\mu$ or contradicts the minimality of~$\mu$ among the walks~$\set{\nu \in F_\alpha}{\omega \prec_\alpha \nu}$.
See \fref{fig:pure}\,(left) for an illustration.
We conclude that~$\lambda = \omega$ has a distinguished arrow~$\beta$ in the direction of~$\alpha$.
\end{proof}

@@

\begin{proof}
In view of Lemma~\ref{lem:distArrowExist}, it remains to prove that each walk of~$F$ contains at most one distinguished arrow in each direction.
Assume that a walk~$\omega$ has two distinguished arrows~$\alpha, \beta$ pointing in the same direction.
Orient~$\omega$ in this same direction and assume without loss of generality that~$\alpha$ appears before~$\beta$ along~$\omega$.
%Note that we also allow a priori~$\alpha, \beta$ to be different occurrences along~$\omega$ of the same arrow of~$Q\blossom_1$.
Let~$\gamma$ be the incoming arrow at~$v \eqdef s(\beta)$ such that~$\gamma\beta \in I$.
Let~$\nu \eqdef \distinguishedWalk{\gamma}{F}$ denote the distinguished walk of~$F$ at~$\gamma$, considered oriented backward~$\gamma$.
We denote by~$\sigma$ the maximal common substring of~$\omega$ and~$\nu$ (it can be reduced to~$\varepsilon_v$).
Note that~$\sigma$ cannot contain~$\alpha$ since otherwise we would have~$\omega \prec_\alpha \nu$ contradicting the assumption that~$\omega = \distinguishedWalk{\alpha}{F}$. 
Since~$\omega$ and~$\nu$ are non-kissing, $\omega$ (resp.~$\nu$) enters~$\sigma$ with an incoming (resp.~outgoing) arrow.
Let~$\mu \eqdef \omega[\,\cdot\,, v] \, \nu[v, \cdot\,]$ be the walk connecting~$s(\omega)$ to~$t(\nu)$ via~$v$, using the prefix of~$\omega$ ending at~$v$ followed by the suffix of~$\nu$ starting at~$v$.
All these notations are illustrated in \fref{fig:pure}\,(right).
We claim that~$\mu$ is non-kissing with any walk of~$F$, contradicting the maximality~of~$F$.

Assume for the sake of contradiction that there is~$\lambda \in F$ such that~$\lambda$ and~$\mu$ are kissing.
Let~$\tau$ be a maximal common substring of~$\lambda$ and~$\mu$ where they kiss.
Since~$\lambda$ does not kiss~$\omega$ nor~$\nu$ (as they all belong to~$F$), we obtain that~$\tau$ contains~$v$ and strictly contains~$\sigma$.
%To prove this claim, observe first that~$\mu$ is non-kissing with~$\omega$ and~$\nu$ (since~$\omega$ and~$\nu$ are non-kissing).
%Consider another walk~$\lambda \in F$ and assume that~$\lambda$ and~$\mu$ are kissing.
%Note that the maximal common substring~$\tau$ of~$\omega$ and~$\lambda$ containing~$v$ is non-empty (otherwise~$\lambda$ would kiss~$\omega$ or~$\nu$) and contains strictly~$\sigma$ (otherwise~$\lambda$ would kiss~$\nu$).
We now distinguish two cases (see \fref{fig:pure}\,(right)):
\begin{enumerate}[(i)]
\item If~$\lambda$ passes through~$\beta$, then it enters~$\tau$ with an outgoing arrow (since it kisses~$\mu$), contradicting the maximality of~$\omega$~in~$\prec_\beta$.
\item If~$\lambda$ passes through~$\gamma$, then it enters~$\sigma$ with an incoming arrow (since~$\tau$ strictly contains~$\sigma$), contradicting the maximality of~$\nu$ in~$\prec_\gamma$. 
\end{enumerate}
We obtained a contradiction in all cases, which shows that~$\mu$ is non-kissing with any other walk~of~$F$.
